\cvsection{Work Experience}
\begin{cventries}

	\cventry
	{Lead Data Scientist (Manager, Lead-Business Intelligence)}
	{Vodafone}
	{Pune, India}
	{July 2021 - Present}
	{
		\begin{justify}
			I work as a technical manager and an individual contributor for ~12 core ML projects. I initiated the entire ML scene and grew the ML ecosystem from scratch for D'n'A vertical.
			\begin{itemize}
				\item Working on GenAI for Text, FBProphet, LSTM, SKTime, Simulation models, Anomaly detection 
				\item Using Google Cloud Platform for all the projects
				\item I only overlook at and manage technical aspects of the project and team. People management is done my some other resource of mine.
				\item Handing around ~5 critical revenue-impacting projects.
			\end{itemize}
		\end{justify}
	}

	\cventry
	{Senior Machine Learning Researcher}
	{Pramati Technologies}
	{Chennai, India}
	{Oct 2019 - Jun 2021}
	{
		\begin{justify}
			\textbf{R'n'D}
			\begin{itemize}
				\item Contributed an optimizer COCOB to Google TensorFlow SIG Addons 
				\item Worked on how to transform a wrapped page and de-wrap it 
				\item Researching on Gradient based Optimizers
			\end{itemize}
			\textbf{Client Projects}
			\begin{itemize}
				\item[] \textit{Healthy Paws}
				\item Role: Need to do a quality check for the scanned documents and write an algorithm to dewrap a scanned document
				\item We successfully developed an algorithm to check quality of the scanned document. We are in the process of developing an algorithm to dewrap an document.
				\item[] \textit{VERANA}
				\item Role: Managed the Data Science team of 2 including myself from Imaginea. Actively worked on their clinical dataset for increasing their coverage and accuracy for their existing scripts.
				\item We worked on some of their existing code and increased their accuracy and coverage percentage. We developed an address extraction script from a given document using NLP.
				\item[] \textit{BAIN}
				\item Role: Responsible for analyzing the CLV and building a Data Analytics dashboard.
				\item The project involves analyzing the survey data and figuring out the CLV. It also entails creating a Tableau Dashboard that analyzes all the features in a single dashboard.
			\end{itemize}
		\end{justify}
	}
	
	\cventry
	{Machine Learning Researcher}
	{}
	{}
	{Oct 2018 - Sep 2019}
	{
		\begin{justify}
			\textbf{R'n'D}
			\begin{itemize}
				\item Worked on Fonduer to incorporate in your pipeline
				\item Natural Image Deniosing using a random pixel image
			\end{itemize}
			\textbf{Client Projects}
			\begin{itemize}
				\item[] \textit{RPX Corporation}
				\item Role: Handled Litigation Likelihood (LitLikelihood) module of the project – from data analysis to production deployment.
				\item In this project, the data (~12M records) requires a lot of transformation where some major errors have been observed leading to a drastic improvement in the prediction accuracy. Therefore, LightGBM has been used here and the model is accepted by the client as well. Other projects under RPX, Imbalance Learning with Probabilistic Scoring with Binary Classification, LDA Topic Clustering.
			\end{itemize}
		\end{justify}
	}
	
	\cventry
	{Added COCOB Optimizer to TensorFlow SIG Addons}
	{Contributor @ Google TensorFlow}
	{India}
	{Aug 2020 - May 2021}
	{
		\begin{justify}
			This optimizer is unique as it is a learning rate free algorithm on SGD which works on a betting framework.
			\begin{itemize}
				\item GitHub Code: \href{https://github.com/tensorflow/addons/blob/master/tensorflow_addons/optimizers/cocob.py}{COCOB Optimizer Link}
				\item Link of the Paper: \href{https://arxiv.org/abs/1705.07795}{https://arxiv.org/abs/1705.07795}
			\end{itemize}
		\end{justify}
	}


	\cventry
	{BPB Publications}
	{Book Author}
	{India}
	{Aug 2019 - Nov 2020}
	{\begin{justify}
			A Cookbook that will help you implement Machine Learning algorithms and techniques by building real-world projects.\\
			Key Features:
			\begin{itemize}
				\item Learn how to handle an entire Machine Learning Pipeline supported with adequate mathematics.
				\item Create Predictive Models and choose the right model for various types of Datasets.
				\item Learn the art of tuning a model to improve accuracy as per Business requirements.
				\item Get familiar with concepts related to Data Analytics with Visualization, Data Science and Machine
				      Learning.
			\end{itemize}
		\end{justify}
	}

	\cventry
	{Arizona State University (ASU) \& National Science Foundation (NSF)}
	{Participant}
	{Part Time}
	{May 2020 - Jun 2020}
	{\begin{flushleft}
			2020 CPS Challenge "Soil Scope -- Mars edition" :\newline Mars 2020 inspired mission scenario for the 2020 NSF CPS Challenge will be a two-week virtual event, emulating an autonomous probe deployment science mission by a rover and drone duo, at the Jezero crater landing site.\newline
			Organizer:\\
			Arizona State University, NASA
		\end{flushleft}}


	
	\cventry
	{Accenture}
	{Associate Software Engineer}
	{Chennai, India}
	{Jan 2017 - Sep 2018}
	{	\begin{flushleft}
			I am working as a Machine Learning Developer at Accenture for multiple Research projects, and few of the research projects won awards, and it has been considered as product by the company.
			\begin{itemize}
				\item Financial Service Development Project (Quartz Development) (Full Time, Managed team size of 2)
				\item Self Learning Credit Approval System (Part time, 3 months)
				\item AI Model Based Risk Management (Part time, 4 months)
				\item Ship and Air Cargo Routing (Part time, 2 months)
				\item Digital Content and Transaction Management using\\ an Artificial Intelligence (AI) based Communication System (Part time, 3 months)
				\item Routing System for Carpool and Drop for the Employees (Part time, 3 months)
			\end{itemize}
		\end{flushleft}
	}

	\cventry
	{HackerOne}
	{Bounty Hunter}
	{Part Time}
	{Jan 2017 - Present}
	{
		\begin{flushleft}
			Found and Resolved Bugs for:
			\begin{itemize}
				\item {Zomato}
			\end{itemize}
		\end{flushleft}
	}

	\cventry
	{PixRead}
	{Creator}
	{India}
	{Dec 2016 - Present}
	{\begin{flushleft}
			One of a kind OCR \& 2D Codes (QR Code, Bar Code, etc...) search engine where the extracted text will
			be searched over a search engine. This will ease all the users to take a picture (which has text) from a
			device and search over different search engines.
		\end{flushleft}}

	\cventry
	{Saltlake Institute of Engineering \& Management}
	{Technical Associate}
	{Kolkata, India}
	{Aug 2015 - Feb 2015}
	{Website Developer \& SEO Professional}


\end{cventries}

% \cventry
% {Job title after promotion} % Job title
% {Corporation} % Organization
% {Location} % Location
% {August 2019 - now}
% {
%   \begin{cvitems} 
% 	\item {Responsibilities}
% 	\end{cvitems}
%  }


% \cventry
% {Job title before your promotion}
% {} % Organization EMPTY
% {} % Location EMPTY
% {somewhere in the past - a while ago} % Date(s)
% {
%   \begin{cvitems}
% 	\item {Old responsibilities}
% 	\end{cvitems}
%  }