\cvsection{Projects}
\begin{cventries}
	\cventry
	{}
	{Bank of America (Quartz Development)}
	{Python, Angular JS}
	{Accenture}
	{\textbf{Problem:} We had multiple tools of different technologies, and we require proficient resource to use the tools. Project was people driven.\newline
		\textbf{Action:} I made a platform for Environment Management team where all the automated scripts (for multiple technologies) \& report generation tools will be placed \& used from a single integrated platform with a simple UI.\newline
		\textbf{Result:} Saved a lot of manual effort, anybody with the access permission can use the tool can execute it using a simple UI with less or no knowledge of the technology, Project became Process driven.
	}
	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}
	\cventry
	{}
	{Self Learning Credit Approval System}
	{Python, ML, H2o.ai, Scikit-learn}
	{Accenture}
	{\textbf{Problem:} Rule based decision for approval of Credit which lead to loss of business.\newline
		\textbf{Action:} I was solely responsible for the development of the Machine Learning Algorithm.\newline
		\textbf{Result:} Accenture took this as a product and demonstrated to the client for identifying bad loans or missed opportunities, enable the bank to mitigate potential risk and opportunities
	}
	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}
	\cventry
	{
	}
	{AI Model Based Risk Management}
	{Azure, Python, H2o.ai}
	{Accenture}
	{\textbf{Problem:} High level of manual effort from Compliance officer for Risk Management to detect valid and type of alerts raised.\newline
		\textbf{Action:} I made an AI based Model using Deep Learning to detect the Alert and type of alert which is performed by Compliance officer.\newline
		\textbf{Result:} Dependency on the compliance officer will decrease, model will be capable to figure out new patterns in the generated alert.
	}
	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{Ship and Air Cargo Routing}
	{Python, Machine Learning}
	{Accenture}
	{\textbf{Problem:} Ship and Air Cargo Routing for Logistics with high traffic and more than expected loading time.\newline
		\textbf{Action:} Used key concepts of algorithm and process Design to optimize the whole system.\newline
		\textbf{Result:} Decreased the time for processing more than 20 seconds which improved the performance and saved huge money.}
	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{Digital Content and Transaction Management using an Artificial Intelligence (AI) based Communication System}
	{Python, Machine Learning, H2o.ai, Scikit-learn}
	{Accenture}
	{\textbf{Problem:} There were no existing intelligent model to predict Disputes of a transaction of a financial institute.\newline
		\textbf{Action:} I have designed a machine learning model which predicts both the dispute and the dispute category of a financial transaction given to the model using a life dataset.\newline
		\textbf{Result:} Accuracy of the model with the live dataset came to be around 92\%. The project is applied for patent by Accenture and will be sold as a product to the clients. This offering is expected to Reduce Annual Billing Disputes Volume by ~30\% i.e. ~330K, lowering Ops Cost by USD 15.3 million and enhancing Customer Experience by guarding them from such dispute prone transactions.
	}

	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{Routing System for CarPool and Drop for the Employees}
	{Python, Machine Learning, H2o.ai, Scikit-learn}
	{Accenture}
	{\textbf{Problem:} There were no existing intelligent model to predict Disputes of a transaction of a financial institute.\newline
		\textbf{Action:}: Created a software using Google Map and some grouping algorithm with considering total cars, total no of seat in each car, last drop should be a male for women security.\newline
		\textbf{Result:} Reduced the entire manual effort form sorting and assigning of the cabs
	}

	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{PixRead}
	{Python}
	{\href{https://github.com/rehanguha/pixread}{\faLink Link}}
	{An Innovative Research Project which helps the users to extract the text from an Image using OCR and other image processing algorithms and search through different Popular Search Engines. Technologies used - OpenCV, Google Tesseract OCR, etc...}

	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{AudioAnalytica}
	{Python, Machine Learning}
	{\href{https://github.com/rehanguha/AudioAnalytica}{\faLink Link}}
	{AudioAnalytica is a no-code platform and audio analytics dashboard.
	This is one of a kind All-in-One Audio analytics platform.
	There were a handful number of solutions who offer an audio analysis and analytics platform for general and not specific to one vertical.
	Dashboard for individuals looking to get insight from audio files and use that knowledge for their business with no knowledge of Audio Processing.
	}

	\begin{center}
		\rule{30mm}{.1mm}
	\end{center}

	\cventry
	{}
	{2D to 3D - Floor Plan}
	{Python, Machine Learning, OpenCV, AR/VR}
	{}
	{2D to 3D - Floor Plan is a tool to convert 2D floor plan to 3D. Later using the output from Python and OpenCV, a virtual reality is created
	that can be interacted by a user. This project easily creates an AR/VR environment without the huge knowledge of 3D model designing.}

	\vspace{5mm}
\end{cventries}