\cvsection{Publications}
\begin{cventries}
    \vspace{3mm}
    \cventry
    {Machine Learning, Credit Risk Scoring}
    {Digital Content and Transaction Management using an Artificial Intelligence (AI) based Communication System}
    {Patent: \href{https://patents.google.com/patent/US20200034842A1/en}{US20200034842A1}}
    {Aug 2018}
    {A system for predicting a non-fraud dispute using an artificial intelligence (AI) based communications system is disclosed. The system may comprise a data access interface to receive instructions historical transaction and disputes data from at least one data source associated with an account issuer. The data access interface may also receive incoming transaction data associated with a transaction from at least one data source associated with an account holder. The system may comprise a processor to predict a likelihood of a non-fraud dispute associated with the transaction by: examining the historical transaction and disputes data; retrieving non-fraud dispute attributes; parsing the incoming transaction data; applying predictive analytics to the incoming transaction data to yield a prediction value; determining that the prediction value meets a predetermined threshold; and generating a predictio for the likelihood of a non-fraud dispute associated with the transaction associated with the account holder to be outputted, via an output interface to a user device.}

    \cventry
    {Data, Numerical}
    {Prime Numbers - 1st One Lac}
    {Dataset: \href{https://github.com/rehanguha/Generating-Prime-Numbers}{\faLink Link}}
    {Jun 2016}
    {Contains 1000 files with 100 prime numbers in each file.}

    \cventry
    {Algorithm, Research, Searching}
    {Grid Searching - Novel way of Searching 2D Array}
    {Journal: \href{https://www.ijcat.com/show.php?vol=volume5&issu=issue1&uid=ijcatr05011005}{\faLink Link}}
    {Jan 2016}
    {Linear/Sequential searching is the basic search algorithm used in data structures. Linear search is used to find a particular element in a
    2D array. It is not compulsory to arrange an array in any order (Ascending or Descending) as in case of 2D binary search. In this paper, I
    present a unique searching algorithm named Grid Search, which helps to search an unsorted 2D Array/Matrix with least time
    complexity and iteration. We also have compared the Grid searching algorithm with Linear Search Algorithm. We used C++ for
    implementation and analysis of CPU time taken by both the algorithms. Results have shown that Grid Searching Algorithm is working
    well for all input values, and it takes lesser time than Sequential Searching in all aspects.}

    \cventry
    {Electronics, Architecture, Railways}
    {Biometric Ticketing System}
    {Patent}
    {Mar 2014}
    {To introduce fingerprint ticketing system in metro railway system by replacing RFID tickets.}

    \cventry
    {Electronics, Architecture, Election}
    {Biometric Voting Machine}
    {Patent}
    {Dec 2014}
    {This machinery function and system is more scientific and real alternative to EVM or Ballot paper with stamp system. In this system
    biometric registration of the voters, voting by biometric identity cards only, no need to make registered voter list before each election,
    identity checking with fingerprint matching, voting with biometric fingerprint impression, auto-locking of each fingerprint identity after
    casting vote, one person can cast only one and his own vote, flexibility of votes to cast his/her vote in different booths (under certain
    conditions), centralize vote counting opportunity are the key functions.}

    \cventry
    {Architecture, Algorithm}
    {Data Security- Multi-Layer Folder Lock Hiding}
    {Patent}
    {Apr 2013}
    {The invention is a computer program, method and process in which the ID-Data is locked with 5 tier protection system and the ID-Data
    also protected from rouge software.}

\end{cventries}